### 2012-12-03 doc/mandc2013/theory_paper/slattery_wilson_evans.tex
updated paper title and keywords

\begin{center}
\textbf{\large \\% 
A SPECTRAL ANALYSIS OF THE DOMAIN DECOMPOSED ADJOINT MONTE CARLO
METHOD FOR LINEAR OPERATOR EQUATIONS}
% 
% First AUTHORS 
%
\\
\setlength{\baselineskip}{14pt}
\textbf{S.R. Slattery and P.P.H. Wilson} \\
Engineering Physics Department \\
University of Wisconsin - Madison  \\
1500 Engineering Dr., Madison, WI 53706 \\
sslattery@wisc.edu; wilsonp@engr.wisc.edu \\

@@

\emph{Key Words}: Monte Carlo domain decomposition MCSA
\end{small} 
\end{quote}

>>>>

\begin{center}
\textbf{\large \\% 
A SPECTRAL ANALYSIS OF THE DOMAIN DECOMPOSED MONTE CARLO METHOD FOR
LINEAR SYSTEMS} 
% 
% First AUTHORS 
%
\\
\setlength{\baselineskip}{14pt}
\textbf{S.R. Slattery and P.P.H. Wilson} \\
Engineering Physics Department \\
University of Wisconsin - Madison  \\
1500 Engineering Dr., Madison, WI 53706 \\
sslattery@wisc.edu; wilsonp@engr.wisc.edu \\

@@

\emph{Key Words}: Monte Carlo, domain decomposition, MCSA
\end{small} 
\end{quote}
